Here is the information we have for the different NA beer offerings so
far.

| product                                        | calories | carbohydrates | protein | fat |
|------------------------------------------------|----------|---------------|---------|-----|
| ATHLETIC FREE WAVE HAZY IPA BEER               | 70       | 16            | 1       | 0   |
| ATHLETIC RUN WILD IPA BEER                     | 65       | 16            | 0       | 0   |
| ATHLETIC UPSIDE DAWN GOLDEN ALE BEER           | 45       | 10            | 1       | 0   |
| BUDWEISER ZERO BEER                            | 50       | 12            | 0       | 0   |
| BUSCH NA BEER                                  | 60       | 12.9          | 0.6     | 0   |
| CLAUSTHALER AMBER NA BEER                      | 75       | 16            | 1.1     | 0   |
| CLAUSTHALER MALT BEVERAGE                      | 92       | 18.8          | 1.4     | 0   |
| CLAUSTHALER DRY HOPPED MALT BEVERAGE           | 26       | 5.6           | 0.5     | 0   |
| CLAUSTHALER SANTA HOLIDAY BREW BEER            | 106.5    | 24.5          | 0.5     | 0   |
| COORS NON ALCOHOLIC MALT BEVERAGE              | 41       | 8             | 1       | 0   |
| GENESEE NA MALT BEVERAGE                       | 70       | 15            | 0.2     | 0   |
| GUINNESS NON ALCOHOLIC DRAUGHT MALT BEVERAGE   | 57.4838  | 12.84932      | 1.4     | 0   |
| HAAKE BECK NA MALT BEVERAGE                    | 70       | 15            | 1       | 0   |
| HEINEKEN 0.0 BEER                              | 74       | 17.1          | 0.9     | 0   |
| ODOULS AMBER NA MALT BEVERAGE                  | 70       | 13            | 1       | 0   |
| ODOULS NA BEER                                 | 60       | 13.3          | 0.7     | 0   |
| OLD MILWAUKEE N A MALT BEVERAGE                | 58       | 12.1          | 0.4     | 0   |
| SAINT PAULI N A MALT BEVERAGE                  | 90       | 23            | 1       | 0   |
| SAMUEL ADAMS JUST THE HAZE HAZY JUICY NON ALCOHOLIC IPA BEER | 98    | 22          | 1.5     | 0   |
| STELLA ARTOIS LIBERTE BEER                     | 63.21429 | 13.92857      | 1.636364| 0   |

We also have the data saved in multiple csv files from Beer Advocate, the beer forum I scraped data from.
Look at scraping.rmd in this repository for information on that.

```{r, message = FALSE}
rm(list = ls())
library(tidyverse)
```

```{r}
# Reading all the csv files that we have, thank you StackOverflow
temp = list.files(pattern="\\.csv$")
for (i in 1:length(temp)) assign(gsub("\\.csv$", "", temp[i]), read.csv(temp[i]))
rm(temp)
```


```{r}
# Making this into one list for easy access
NABeersRatings = list("AthleticFreeWaveHazyIPABeer" = AthleticFreeWaveHazyIPABeer,
                      "AthleticRunWildIPABeer" = AthleticRunWildIPABeer,
                      "AthleticUpsideDawnGoldenAleBeer" = AthleticUpsideDawnGoldenAleBeer,
                      "BudweiserZeroBeer" = BudweiserZeroBeer,
                      "BuschNABeer" = BuschNABeer,
                      "ClausthalerAmberNA" = ClausthalerAmberNA,
                      "ClausthalerDryHoppedMaltBeverage" = ClausthalerDryHoppedMaltBeverage,
                      "ClausthalerMaltBeverage" = ClausthalerMaltBeverage,
                      "ClausthalerSantaHolidayBrewBeer" = ClausthalerSantaHolidayBrewBeer,
                      "CoorsNonAlcoholicMaltBeverage" = CoorsNonAlcoholicMaltBeverage,
                      "GeneseeNAMaltBeverage" = GeneseeNAMaltBeverage,
                      "GuinnessNonAlcoholicDraughtMaltBeverage" = GuinnessNonAlcoholicDraughtMaltBeverage,
                      "HaakeBeckNAMaltBeverage" = HaakeBeckNAMaltBeverage,
                      "Heineken00Beer" = Heineken00Beer,
                      "ODoulsAmberNAMaltBeverage" = ODoulsAmberNAMaltBeverage,
                      "ODoulsNABeer" = ODoulsNABeer,
                      "OldMilwaukeeNAMaltBeverage" = OldMilwaukeeNAMaltBeverage,
                      "SaintPauliNAMaltBeverage" = SaintPauliNAMaltBeverage,
                      "SamuelAdamsJustTheHazeJuicyNonAlcoholicIPABeer" = SamuelAdamsJustTheHazeJuicyNonAlcoholicIPABeer,
                      "StellaArtoisLiberteBeer" = StellaArtoisLiberteBeer)

# Preparing the data for PCA
NABeerPCAData = data.frame(
  product = c(
    "Athletic Free Wave",
    "Athletic Run Wild",
    "Athletic Upside Dawn",
    "Budweiser Zero",
    "Busch NA",
    "Clausthaler Amber",
    "Clausthaler Malt Beverage",
    "Clausthaler Dry Hopped",
    "Clausthaler Santa Holiday Brew",
    "Coors Edge",
    "Genesee Non Alcoholic",
    "Guinness Non Alcoholic Draught",
    "Haake Beck Non Alcoholic",
    "Heineken 0.0",
    "O'Doul's Amber",
    "O'Doul's NA",
    "Old Milwaukee NA",
    "St. Pauli NA",
    "Samuel Adams Just The Haze",
    "Stella Artois Liberte"),
  calories = c(70, 65, 45, 50, 60, 75, 92, 26, 106.5, 41, 70, 57.4838, 70, 74, 70, 60, 58, 90, 98, 63.21429),
  carbohydrates = c(16, 16, 10, 12, 12.9, 16, 18.8, 5.6, 24.5, 8, 15, 12.84932, 15, 17.1, 13, 13.3, 12.1, 23, 22, 13.92857),
  protein = c(1, 0, 1, 0, 0.6, 1.1, 1.4, 0.5, 0.5, 1, 0.2, 1.4, 1, 0.9, 1, 0.7, 0.4, 1, 1.5, 1.636364),
  look = c(map(NABeersRatings, ~mean(.$look, na.rm = T)) %>% unlist()),
  smell = c(map(NABeersRatings, ~mean(.$smell, na.rm = T)) %>% unlist()),
  taste = c(map(NABeersRatings, ~mean(.$taste, na.rm = T)) %>% unlist()),
  feel = c(map(NABeersRatings, ~mean(.$feel, na.rm = T)) %>% unlist()),
  overall = c(map(NABeersRatings, ~mean(.$overall, na.rm = T)) %>% unlist())
)

NABeerPCAData$product = factor(NABeerPCAData$product)
```

Now we can run a PCA on this data.

```{r}
NABeerPCA = prcomp(NABeerPCAData[2:9], scale = T)
```

Let us plot this

```{r}
# For making PCA biplots
# install.packages("factoextra")
library(factoextra)

# for making text labels
# install.packages("ggrepel")
library(ggrepel)

# for adding images
# install.packages("ggimage")
library(ggimage)

#   install.packages("magick")
library(magick)
```

I want to add images into the mix.
```{r}
logos = c(paste0("R:/Data/Users/sapta/Downloads/MS - Marketing Analytics - Class Downloads/2023 FALL/Capstone Project/Material/Logos/", names(NABeersRatings), ".png"))
```

```{r}
NABeerPCAViz = fviz_pca_biplot(NABeerPCA,
                geom = "point",
                col.var = NA) +
  geom_image(aes(image = logos),
             size = 0.2,
             alpha = 0.5)

NABeerPCAViz
```
